EuPPollNet: A European database of plant-pollinator networks

### 2024-04-15 Manuscript/Ms.qmd
taxonomic coverage text

@@

The database contains a total of `r prettyNum(plant_spp_number, big.mark=",")` plant and `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator species. The database coverage of all flowering plant species occurring in Europe is `r format(round(plant_coverage, 2), nsmall=2)`% (**Figure 4**), with an average coverage of `r format(round(mean_plant_fam_cov, 2), nsmall=2)`% at the plant family level. Approximately, half of the plant families have at least one species with interaction records (`r format(round(percent_plant_fam_with_data, 2), nsmall=2)`%), and the presence or absence of interaction data for the different plant species seems not to follow a statistically relevant phylogenetic pattern ($\lambda$ = `r format(round(lambda_phylosig_plants, 2), nsmall=2)`; _P_ = `r format(round(p_phylosig_plants, 2), nsmall=2)`).

Pollinators:

@@

**Figure S1**

Provide number of species per taxonomic group and number of interactions

>>>>

#Load pollinator coverage
bee_coverage = readRDS("../Data/Manuscript_info/bee_coverage.RData")
syrphid_coverage = readRDS("../Data/Manuscript_info/syrphid_coverage.RData")
lepidoptera_coverage = readRDS("../Data/Manuscript_info/lepidoptera_coverage.RData")
#Check percentage of interactions from bees with and without apis
#Check percentage of bees in the database
bee_fam = c("Apidae", "Megachilidae", "Halictidae",
            "Andrenidae", "Colletidae", "Melittidae")
all_rows = data %>% nrow(.)
#
bee_rows = data %>%
filter(Pollinator_family %in% bee_fam) %>% 
nrow(.)
#Bee interactions
bee_interactions_percent = bee_rows/all_rows *100
#Eclude now apis
bee_rows_non_apis = data %>%
filter(Pollinator_family %in% bee_fam) %>% 
filter(Pollinator_accepted_name == "Apis mellifera") %>% 
nrow(.)
#
bee_interactions_non_apis_percent = bee_rows_non_apis/bee_rows *100

#Coverage across bee genera
d1 = readRDS("../Data/Manuscript_info/bee_data.RData")
all_rows_bees = d1 %>%  
filter(fam_group == "a") %>% 
nrow(.)
#
data_bees = d1 %>%  
filter(fam_group == "a") %>% 
mutate(Percent = case_when(is.na(Percent) ~ 0, TRUE ~ Percent)) %>% 
filter(Percent > 0) %>% 
nrow(.)
#
bee_genera_percent_coverage = data_bees/all_rows_bees
#Check average coverage across bee genera
average_coverage_bee_genera = d1 %>% 
filter(fam_group == "a") %>% 
mutate(Percent = case_when(is.na(Percent) ~ 0, TRUE ~ Percent)) %>% 
ungroup() %>% 
summarise(average_coverage_bee_genera = mean(Percent)) %>% 
pull()

#Calculate phylogenetic signal of presence-absence information
##Read data and plot it
tree = readRDS("../Data/Manuscript_info/bee.tree100.rds")
##Create binary trait to calculate phylo
phylo_trait = d1 %>% 
filter(fam_group == "a") %>% 
mutate(Percent = case_when(is.na(Percent) ~ 0, TRUE ~ Percent)) %>% 
mutate(categorical = case_when(Percent > 0 ~ 1, TRUE ~ 0)) %>% 
ungroup() 
##Conduct left join to tibble of tip labels to organise order
v = tibble(Genus1 = tree$tip.label) %>% 
mutate(Genus1 = str_to_title(word(Genus1,1,sep = "_")))
#
v1 = left_join(v, phylo_trait)
#
v2 = v1$categorical
names(v2) = tree$tip.label
#
phylo_signal_bees = phylosig(tree, v2, method="lambda", test=TRUE)
lambda_phylosig_bees = phylo_signal_bees$lambda
p_phylosig_bees = phylo_signal_bees$P

@@

The database contains a total of `r prettyNum(plant_spp_number, big.mark=",")` plant and `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator species. The database coverage of all flowering plant species occurring in Europe is `r format(round(plant_coverage, 2), nsmall=2)`% (**Figure 4**), with an average coverage of `r format(round(mean_plant_fam_cov, 2), nsmall=2)`% at the plant family level. Approximately, half of the plant families have at least one species with interaction records (`r format(round(percent_plant_fam_with_data, 2), nsmall=2)`%), and the presence or absence of interaction data for the different plant species seems not to follow a statistically relevant phylogenetic pattern ($\lambda$ = `r format(round(lambda_phylosig_plants, 2), nsmall=2)`; _P_ = `r format(round(p_phylosig_plants, 2), nsmall=2)`). The coverage of the main taxonomic groups of pollinators at European level is `r format(round(bee_coverage, 2), nsmall=2)`% for bees, `r format(round(syrphid_coverage, 2), nsmall=2)`% for syrphids and `r format(round(lepidoptera_coverage, 2), nsmall=2)`% for butterflies (see **Figure S1** for coverage at the family level for bees and butterflies, and at the subfamily level for syrphids). Bees constitute `r format(round(bee_interactions_percent, 2), nsmall=2)`% of the interactions of the database, and `r format(round(bee_interactions_non_apis_percent, 2), nsmall=2)`% of the interactions when excluding honey bees.

`r format(round(bee_genera_percent_coverage, 2), nsmall=2)`% of bee genera have at least one species with interaction records within the database and the average coverage at the genus level is `r format(round(average_coverage_bee_genera, 2), nsmall=2)`%. Notably, the presence or absence of interactions records seems or not seems to follow any sort of phylogenetic signal (($\lambda$ = `r format(round(lambda_phylosig_bees, 2), nsmall=2)`; _P_ = `r format(round(p_phylosig_bees, 2), nsmall=2)`)).

@@
